The Distributed Nature of Copycat..? (WIP)

### 2017-11-17 papers/paper.tex
WIP

\begin{abstract}
We investigate FARG architectures in general, and Copycat in particular.  One of the foundations of those models is the \emph{Parallel Terraced Scan}--a psychologically-plausible model that enables a system to fluidly move between different modes of processing.  Previous work has modeled decision-making under Parallel Terraced Scan by using a central variable of \emph{Temperature}.

@@

And ten minutes later, it was done.
The "meta" formula performs as well as the "best" formula on the "ijjkkk" problem, which I consider the most novel.
Interestingly, I noticed that the paramterized formulas aren't as good on this problem. What did I parameterize them for? Was it well justified?

>>>>

\begin{abstract}
    We investigate the distributed nature of computation in a FARG architecture, Copycat. 
    One of the foundations of those models is the \emph{Parallel Terraced Scan}--a psychologically-plausible model that enables a system to fluidly move between different modes of processing.  
    Previous work has modeled decision-making under Parallel Terraced Scan by using a central variable of \emph{Temperature}. 
    However, it is unlikely that this design decision accurately replicates the processes in the human brain.

    Additionally, Copycat and other FARG architectures have incredible high rates of unscientific inquiry.
    Specifically, Copycat uses many undocumented formulas and magic numbers, some of which have been parameterized to fix particular problems at the expense of performing worse on others.
    This paper aims to add a framework for conducting so-called "Normal" science with Copycat, in the hopes of making our findings more concrete.

@@

And ten minutes later, it was done.
The "meta" formula performs as well as the "best" formula on the "ijjkkk" problem, which I consider the most novel.
Interestingly, I noticed that the paramterized formulas aren't as good on this problem. What did I parameterize them for? Was it well justified?
(Probably not)
